Learning by Teaching a Robot: the Case of Handwriting

### 2015-07-08 main.tex
Henry Results

\begin{abstract}

    Robots for education are not limited to support ICT teaching, and robots are
    finding new ways to enter and blend in the classroom. This article reports
    on such a new paradigm for educative robots, that involves \emph{learning by
    teaching} and strong \emph{social engagement} to help children struggling
    with handwriting. Our system relies on machine-learning and child-robot
    interaction with a small humanoid robot, and we present several real-world
    studies in schools and with occupational therapists that led us to promising
    initial results.

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{A Different Paradigm for Educative Robots}

@@

In all sessions, Diego was fully focused on the activity during forty minutes up to one
hour. In total, he provided 154 letters as demonstration.\\

@@

Since the robot was learning from scratch, each time Henry succeeded to make his
demonstrations accepted by it, the improvement of its handwriting was
obvious~\ref{learning_6_demos},~\ref{henry_distances}.
Therefor, Henry quickly enter in an self-rewarding game where the rewards were
the improvement of the robot. In total, over the three last sessions he provided 99
demonstrations of number shapes to the robot.

>>>>

\begin{abstract}
    TDB
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{A different paradigm for educative robots}

@@

In all sessions, Diego was fully focused on the activity during forty minutes up to one
hour. In total, he provided X letters as demonstration.\\

@@

Since the robot was learning from scratch, each time Henry succeeded to make his
demonstrations accepted by it, the improvement of its handwriting was
obvious~\ref{learning_6_demos},~\ref{henry_distances}.
Therefor, Henry quickly enter in an self-rewarding game where the rewards were
the improvement of the robot. In total, over the four sessions he provided X
demonstrations of number shapes to the robot.
